---
title:  "Homework 1"
author: "Rene Gutierrez"
date:   "4/5/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
\newcommand{\erf}{\text{erf}}
\newcommand{\dV}{\mathbb{V}}
\newcommand{\dE}{\mathbb{E}}
\newcommand{\dP}{\mathbb{P}}
\newcommand{\Nd}{\text{N}}
\newcommand{\Bd}{\text{Binomial}}
\newcommand{\sgs}{\sigma^2}


## Homework 1

### Problem 1

1. Derive $\dV[\alpha X] = \alpha^2 \dV[X]$

$$
\begin{aligned}
\dV[\alpha X] 
  &= \dE[(\alpha X)^2] - (\dE[\alpha X])^2 \\
  &= \dE[\alpha^2 X] - (\alpha\dE[X])^2 \\
  &= \alpha^2 \dE[X] - \alpha^2\dE[X]^2 \\
  &= \alpha^2 (\dE[X] - \dE[X]^2) \\
  &= \alpha^2 \dV[X] \\
\end{aligned}
$$

2. Prove that if $X$ and $Y$ are independent, then we have

$$\dV[X+Y] = \dV[X] + \dV[Y]$$

$$
\begin{aligned}
\dV[X+Y] 
  &= \dE[(X+Y)^2] - (\dE[X+Y])^2 \\
  &= \dE[X^2 + 2 XY + Y^2] - (\dE[X] + \dE[Y])^2  \\
  &= \dE[X^2] + 2\dE[XY] + \dE[Y^2] - \dE[X]^2 - 2\dE[X]\dE[Y] - \dE[Y]^2  \\
  &= \dE[X^2] + 2\dE[X]\dE[Y] + \dE[Y^2] - \dE[X]^2 - 2\dE[X]\dE[Y] - \dE[Y]^2 &\text{by independence}  \\
  &= \dE[X^2]  - \dE[X]^2 + \dE[Y^2] - \dE[Y]^2\\
  &= \dV[X] + \dV[Y]\\
\end{aligned}
$$

## Problem 2

Let $X \sim \Bd(n, p)$. We know

$$\dE[X] = n p $$
$$ \dV[X] = n p (1-p) $$
Use these results to calculate $\dE[X^2]$. Write the results as a polynomial of $n$.

We have that

$$\dV[X] = \dE[X^2] - \dE[X]^2$$
then

$$
\begin{aligned}
\dE[X^2] 
  &= \dV[X] + \dE[X]^2 \\
  &= np(1-p) + (np)^2 \\
  &= pn^2 + p(1-p)n
\end{aligned}
$$

## Problem 3

Let $X \sim \Nd(\mu, \sgs)$. Fill in the details in the derivation

$$
\begin{aligned}
\dP(\mu - \eta \sigma \leq X \leq \mu + \eta \sigma) 
  &= F_X(\mu + \eta \sigma) - F_X(\mu - \eta \sigma) \\
  &= F_X(\mu + \eta \sigma) - F_X(\mu - \eta \sigma) \\
  &= \frac{1}{2} \left( 1 + \erf\left(\frac{\mu + \eta \sigma - \mu}{\sqrt{2} \sigma}\right) \right) - \frac{1}{2} \left( 1 +  \erf\left(\frac{\mu - \eta \sigma - \mu}{\sqrt{2} \sigma}\right) \right) \\
  &= \frac{1}{2} + \frac{1}{2} \erf\left(\frac{\eta}{\sqrt{2}}\right) - \frac{1}{2} - \frac{1}{2} \erf\left(\frac{-\eta}{\sqrt{2} \sigma}\right) \\
  &= \frac{1}{2} \left( \erf\left(\frac{\eta}{\sqrt{2}}\right) - \erf\left(\frac{- \eta}{\sqrt{2} \sigma}\right) \right) \\
  &= \frac{1}{2} \left( \erf\left(\frac{\eta}{\sqrt{2}}\right) + \erf\left(\frac{\eta}{\sqrt{2} \sigma}\right) \right) \\
  &= \erf \left(\frac{\eta}{\sqrt{2}} \right)
\end{aligned}
$$

## Problem 4

1. Compute $\dE[X]$

Note that:

$$\dE[X | Y=m] = mp $$

then

$$
\begin{aligned}
\dE[X] &= \dE[\dE[X|Y]] &\text{by law of total expectation} \\
  &= \dE[Yp] \\
  &= p\dE[Y] \\
  &= p(np) \\
  &= np^2 \\
\end{aligned}
$$

2. Compute $\dE[XY]$

$$
\begin{aligned}
\dE[XY] &= \dE[\dE[XY|Y]] &\text{by law of total expectation} \\
  &= \dE[Y\dE[X|Y]] &\text{by by linearity} \\
  &= \dE[Y(Yp)] \\
  &= p\dE[Y^2] \\
  &= p(pn^2 + p(1-p)n) \\
  &= p^2n^2 + p^2(1-p)n \\
\end{aligned}
$$

## Problem 5

1. Known variance:

```{r p5-1}
### Sampling Set-up
seed <- 1
n    <- 10
M    <- 500000
m    <- 0.6
s    <- 1.3


### Draws the samples
x <- matrix(rnorm(n = n * M, m, s),
            nrow = M,
            ncol = n)

mea    <- rowMeans(x)

conInt <- cbind(mea - 1.96 * s / sqrt(n), mea + 1.96 * s / sqrt(n))

inConInt <- (conInt[, 1] < m) * (conInt[, 2] > m)

proIn    <- sum(inConInt) / M

```

The estimate of the probability that the exact 95\% confidence interval contains $\mu^{true}$ is: `r proIn`.

2. Unknown variance:

```{r p5-2}
es <- apply(x, 1, var)
conInt <- cbind(mea - 1.96 * es / sqrt(n), mea + 1.96 * es / sqrt(n))

inConInt <- (conInt[, 1] < m) * (conInt[, 2] > m)

proIn    <- sum(inConInt) / M

```

<<<<<<< HEAD
The estimate of the probability that the approximate 95\% confidence interval contains $\mu^{true}$ is: `r proIn`.
=======
The estimate of the probability that the approximate 95\% confidence interval contains $\mu^{true}$ is: `r proIn`.








































    
    
    
    
    
    
    
    
    
    
    
    






















>>>>>>> 8092c9d729c528ec625c51ca532d62258caccd95
