---
title:  "Homework 2"
author: "Rene Gutierrez"
date:   "4/10/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
\newcommand{\erf}{\text{erf}}
\newcommand{\dV}{\mathbb{V}}
\newcommand{\dE}{\mathbb{E}}
\newcommand{\dP}{\mathbb{P}}
\newcommand{\Nd}{\text{N}}
\newcommand{\Bd}{\text{Binomial}}
\newcommand{\gss}{\sigma^2}


## Homework 2

### Problem 1

a. Express $F_Y(y)$ in terms of $F_X(x)$.

$$
\begin{aligned}
  F_Y(y) 
    &= \dP(Y<y)         \\
    &= \dP(\alpha X <y) \\
    &= \dP(X <\frac{y}{\alpha}) \\
    &= F_X \left( \frac{y}{\alpha} \right)
\end{aligned}
$$

a. Express $f_Y(y)$ in terms of $f_X(x)$.

$$
\begin{aligned}
  f_Y(y) 
    &= \frac{d}{dy} F_Y(y)                              \\
    &= \frac{d}{dy} F_X \left( \frac{y}{\alpha} \right) \\
    &= f_X \left( \frac{y}{\alpha} \right) \frac{1}{\alpha} \\
\end{aligned}
$$

### Problem 2

Suppose	$X$ and	$Y$ are	independent,	and $X ~	N(\mu_1,	\gss_1)$	and	$X + Y ~	N(\mu_2,	\gss_2)$.

then the characteristic function of $X$ and $X+Y$ are given by:

$$\phi_X(t) = \exp \left( \mu_1 t + \frac{\gss_1 t^2}{2} \right)$$
and
$$\phi_{X+Y}(t) = \exp \left( \mu_2 t + \frac{\gss_2 t^2}{2} \right)$$
respectively. We also have that the characteristic function of $X+Y$ is given by:
$$
\begin{aligned}
  \phi_{X+Y}(t) 
    &= \dE[e^{it(Y+X)}]       \\
    &= \dE[e^{itY}e^{itX}] \\
    &= \dE[e^{itY}]\dE[e^{itX}] &\text{by independence}\\
    &= \phi_Y(t) \phi_X(t) \\
  \end{aligned}
$$
then:
$$ \exp \left( \mu_2 t + \frac{\gss_2 t^2}{2} \right) = \phi_Y(t) \left( \mu_1 t + \frac{\gss_1 t^2}{2} \right)$$
then:
$$
\begin{aligned}
  \phi_Y(t) 
    &= \exp \left( \mu_2 t + \frac{\gss_2 t^2}{2} \right) 
       \exp \left( -\mu_1 t - \frac{\gss_1 t^2}{2} \right) \\
    &= \exp \left( (\mu_2-\mu_1) t + \frac{(\gss_2 - \gss_1) t^2}{2} \right)
  \end{aligned}
$$
therefore:
$$ Y \sim \Nd (\mu_2-\mu_1, \gss_2 - \gss_1) $$

### Problem 3

a.

$$
\begin{aligned}
  \dE[|X|] 
    &= \int_{-\infty}^{\infty} |x| \frac{1}{\sqrt{2 \pi}}\exp \left(-\frac{x^2}{2}\right)dx \\
    &= \int_{-\infty}^{0} -x \frac{1}{\sqrt{2 \pi}}\exp \left(-\frac{x^2}{2}\right)dx        
     + \int_{0}^{\infty} x \frac{1}{\sqrt{2 \pi}}\exp \left(-\frac{x^2}{2}\right)dx \\
    &= -\int_{0}^{\infty} -x \frac{1}{\sqrt{2 \pi}}\exp \left(-\frac{x^2}{2}\right)dx        
     + \int_{0}^{\infty} x \frac{1}{\sqrt{2 \pi}}\exp \left(-\frac{x^2}{2}\right)dx \\
     &= 2\int_{0}^{\infty} x \frac{1}{\sqrt{2 \pi}}\exp \left(-\frac{x^2}{2}\right)dx \\
     &= \frac{2}{\sqrt{2 \pi}} \int_{0}^{\infty} x \exp \left(-\frac{x^2}{2}\right)dx \\
     &= \sqrt{\frac{2}{\pi}} \int_{0}^{\infty} x \exp \left(-\frac{x^2}{2}\right)dx \\
     &= \sqrt{\frac{2}{\pi}} \int_{0}^{\infty} e^{-y}dy &\text{where} \quad y = \frac{x^2}{2} \\
     &= \sqrt{\frac{2}{\pi}} \left[ -e^{-y}\right|_0^{\infty} \\
     &= \sqrt{\frac{2}{\pi}} 
  \end{aligned}
$$

b. 

$$
\begin{aligned}
  \dE[|X|^3] 
     &= 2\int_{0}^{\infty} x^3 \frac{1}{\sqrt{2 \pi}}\exp \left(-\frac{x^2}{2}\right)dx \\
     &= \frac{2}{\sqrt{2 \pi}} \int_{0}^{\infty} x^3 \exp \left(-\frac{x^2}{2}\right)dx \\
     &= \sqrt{\frac{2}{\pi}} \left( \left[ -x^2 \exp \left(-\frac{x^2}{2}\right)  \right|_0^\infty
      + \int_{0}^{\infty} 2x^2 \exp \left(-\frac{x^2}{2}\right)dx \right)
     & \text{where } u(x)=x^2 \text{ and } v(x)= x \exp \left(-\frac{x^2}{2}\right) \\
     &= 2 \sqrt{\frac{2}{\pi}} \int_{0}^{\infty} x^2 \exp \left(-\frac{x^2}{2}\right)dx \\
     &= 2 \sqrt{\frac{2}{\pi}} \left( \left[ -x \exp \left(-\frac{x^2}{2}\right)  \right|_0^\infty
      + \int_{0}^{\infty} x \exp \left(-\frac{x^2}{2}\right)dx \right)
     & \text{where } u(x)=x \text{ and } v(x)= x \exp \left(-\frac{x^2}{2}\right) \\
     &= 2 \sqrt{\frac{2}{\pi}}
  \end{aligned}
$$

c.

$$
\begin{aligned}
  \dE[|X|^3] 
     &= 2\int_{0}^{\infty} x^4 \frac{1}{\sqrt{2 \pi}}\exp \left(-\frac{x^2}{2}\right)dx
     & \text{by symmetry}\\
     &= \frac{2}{\sqrt{2 \pi}} \int_{0}^{\infty} x^4 \exp \left(-\frac{x^2}{2}\right)dx \\
     &= \sqrt{\frac{2}{\pi}} \left( \left[ -x^3 \exp \left(-\frac{x^2}{2}\right)  \right|_0^\infty
      + \int_{0}^{\infty} 3x^3 \exp \left(-\frac{x^2}{2}\right)dx \right)
     & \text{where } u(x)=x^3 \text{ and } v(x)= x \exp \left(-\frac{x^2}{2}\right) \\
     &= 3 \sqrt{\frac{2}{\pi}} \int_{0}^{\infty} x^3 \exp \left(-\frac{x^2}{2}\right)dx \\
     &= 3 \sqrt{\frac{2}{\pi}} \sqrt{\frac{\pi}{2}} 
     &\text{from last excersice} \\
     & = 3
  \end{aligned}
$$

### Problem 4

Let

$$ C := \text{Your initial selection is correct.} $$
$$ E := \text{The box you open is empty.} $$
Call $X=$ Profit if you don't switch and $Y=$ Profit if you switch. Then:

$$\dE[X] = 200 \dP(C\mid E) + 0 \dP(C^c\mid E)$$
and
$$\dE[Y] = -5 \dP(C\mid E) + 200 \dP(C^c\mid E) $$
Now, we have that
$$ \dP(C \mid E) = \frac{\dP(E \mid C)\dP(C)}{\dP(E)}$$
by Bayes Theorem. Also note that:
$$ \dP(E \mid C) = 1 $$
since, if you select the right door, the other 2 are empty. Similarly,
$$ \dP(E \mid C^c) = \frac{1}{2} $$
since if you don't select the right door, one of the is empty. Also
$$ \dP(E) = \dP(E \mid C) \dP(C) + \dP(E \mid C^c) \dP(C^c) =  1 \frac{1}{3} + \frac{1}{2} \frac{2}{3} = \frac{2}{3} $$
Therefore:
$$ \dP(C \mid E) = \frac{\frac{1}{3}}{\frac{2}{3}} = \frac{1}{2} $$
given this result, you should not pay to switch since:

$$ \dE[X]=100 $$
and
$$ \dE[Y]=97.5 $$

```{r Simulation Modified Monty Hall}
### Number Simulated Games
sim <- 100000
### Number of Invalid Games
inv <- 0
### Number of Times you are correct/incorrect given a valid game
cor <- 0
inc <- 0
for (s in 1:sim){
  car <- as.vector(rmultinom(1, 1, c(1/3, 1/3, 1/3))) # Car location
  sel <- as.vector(rmultinom(1, 1, c(1/3, 1/3, 1/3))) # Initial door Selection
  ope <- c(1, 2, 3)[!(sel==1)][as.vector(rmultinom(1, 1, c(1/2, 1/2)))] # Open door
  if(car[ope] == 1){ # The Game is Invalid
    inv <- inv + 1
  } else {
    if(car[sel==1] == 1){
      cor <- cor + 1
    } else {
      inc <- inc + 1
    }
  }
}
proSta <- 200 * cor / (sim - inv)
proSwi <- 200 * inc / (sim - inv) - 5 * cor / (sim - inv)
```

### Problem 5

Using the odd extension with:
$$
u(x, 0) = 
\begin{cases}
1, & \text{if } x>c_0   \\
0, & \text{if } x\leq c_0
\end{cases}
$$

the initial boundary value problem IBVP is transformed to an Initial Value Problem IVP as follows:

$$
\begin{cases}
  u_t = \frac{1}{2} u_{xx} \\
  u(x, 0) =
  \begin{cases}
    1,  & \text{if } x>c_0               \\
    0,  & \text{if } -c_0 \leq x \leq c_0 \\
    -1, & \text{if } x<-c_0   
  \end{cases}
\end{cases}
$$
Then the general solution is given by:

$$
\begin{aligned}
  u(x, t)
  &= \frac{1}{\sqrt{4 \pi a t}} \int_{-\infty}^\infty \exp \left( \frac{-\xi^2}{4at} \right) f(x-\xi) d\xi
\end{aligned}
$$
then, noting that:
$$
f(x - \xi) =
  \begin{cases}
    -1, & \text{if } \xi > c_0 + x   \\
    0,  & \text{if } x - c_0 \leq \xi \leq \ x + c_0  \\
    1,  & \text{if } \xi < x - c_0            \\
  \end{cases}
$$
then

$$
\begin{aligned}
  u(x, t)
  &= \frac{1}{\sqrt{2 \pi  t}} \int_{-\infty}^\infty \exp \left( \frac{-\xi^2}{2t}f(x-\xi) \right) d\xi \\
  &= \frac{1}{\sqrt{2 \pi  t}} \left(
    \int_{-\infty}^{x-c_0} \exp \left( \frac{-\xi^2}{2t} \right) d\xi
  - \int_{x+c_0}^{\infty} \exp \left( \frac{-\xi^2}{2t} \right) d\xi
  \right) \\
  &= F_X(x-c_0) - 1 + F_X(x+c_0) 
  &\text{for } X \sim \Nd(0,\sqrt{t}) \\
  &= \frac{1}{2} \left(1  + \erf \left( \frac{x - c_0}{\sqrt{2t}} \right) \right)
   + \frac{1}{2} \left(1  + \erf \left( \frac{x + c_0}{\sqrt{2t}} \right) \right) -1 \\
  &= \frac{1}{2} \left(\erf \left( \frac{x - c_0}{\sqrt{2t}} \right) + \erf \left( \frac{x + c_0}{\sqrt{2t}} \right) \right)
\end{aligned}
$$
























